Choosing climate forcing for numerical simulations of the Cordilleran ice sheet

### 2013-02-21 sections/results.tex
Fixed a typo

Using climate forcing from WordClim data and the NCEP/NCAR, ERA-Iterim, CFSR and NARR reanalyses described in section~\ref{sec:climate} and the ice sheet model described in section~\ref{sec:model}, we run simulations of glacial inception and growth of the Cordilleran ice sheet using different temperature offsets.

>>>>

Using climate forcing from WorldClim data, the NCEP/NCAR, ERA-Iterim, CFSR and NARR reanalyses described in section~\ref{sec:climate} and the ice sheet model described in section~\ref{sec:model}, we run simulations of glacial inception and growth of the Cordilleran ice sheet using different temperature offsets.
